Delayed effects of climate on vital rates leads to demographic divergence in Amazonian forest fragments

### 2021-06-17 doc/paper.Rmd
uninculde code chunks

```{r}
#get 84% CI around intercepts
withr::with_dir(here::here(), {
  tar_load(c(s_cf, s_1ha))
})
source(here::here("R", "pull_ci.R"))
pull_ci(s_cf)
pull_ci(s_1ha)
rm(s_cf, s_1ha)
```

@@

```{r}
#get 84% CI around intercepts
withr::with_dir(here::here(), {
  tar_load(c(g_cf, g_1ha))
})
pull_ci(g_cf, digits = 2)
pull_ci(g_1ha, digits = 2)
rm(g_cf, g_1ha)
```

@@

```{r}
#get 84% CI around intercepts
withr::with_dir(here::here(), {
  tar_load(c(f_cf, f_1ha))
})
pull_ci(f_cf, digits = 4)
pull_ci(f_1ha, digits = 4)
rm(f_cf, f_1ha)
```

>>>>

```{r include=FALSE}
#get 84% CI around intercepts
withr::with_dir(here::here(), {
  tar_load(c(s_cf, s_1ha))
})
source(here::here("R", "pull_ci.R"))
pull_ci(s_cf)
pull_ci(s_1ha)
rm(s_cf, s_1ha)
```

@@

```{r include=FALSE}
#get 84% CI around intercepts
withr::with_dir(here::here(), {
  tar_load(c(g_cf, g_1ha))
})
pull_ci(g_cf, digits = 2)
pull_ci(g_1ha, digits = 2)
rm(g_cf, g_1ha)
```

@@

```{r include=FALSE}
#get 84% CI around intercepts
withr::with_dir(here::here(), {
  tar_load(c(f_cf, f_1ha))
})
pull_ci(f_cf, digits = 4)
pull_ci(f_1ha, digits = 4)
rm(f_cf, f_1ha)
```
